\documentclass[12pt]{article}
\usepackage[margin=1in]{geometry}
\usepackage{fancyhdr}
\usepackage{hyperref}

\pagestyle{fancy}
\fancyhf{}
\cfoot{\thepage}
\lhead{VRC Technical Rider}
\rhead{18x18az}

%\usepackage{draftwatermark}
%\SetWatermarkText{DRAFT}
%\SetWatermarkScale{5}

\title{18x18az\\VRC Technical Rider}
\author{v1.3.0}
\date{Revised \today}
% TODO: add logo somewhere
% make logo watermark? or is that too much
\begin{document}
\maketitle
Thank you for considering hosting an event with us!
In this document you will find information such as what we need from the venue as well as our pricing options.
If you have any questions or comments, please do not hesitate to contact us.
\tableofcontents
\pagebreak
\section{Our Services}
\subsection{Base Package}
Our base package, costing \$200, includes:
\begin{itemize}
    \item Field control for two (2) competition fields
    \item Field control for one (1) skills field
    \item Livestream equipment and operation
    \item Tournament Manager (TM) operation
    \item Scoring tablets
    \item Audiovisual equipment
\end{itemize}

\noindent We will livestream the event to our YouTube channel, located at \\\url{http://youtube.18x18az.org}.

\subsection{Large Event Package}
We can support field control for a third competition field and a second skills field for an additional \$100 fee.
This will bring up the total number of supported fields to three (3) competition fields and two (2) skills fields.

\subsection{Pipe and Drape}
We can loan our set of pipe and drape (70 feet) for an additional \$150 fee.
Additionally by requesting pipe and drape, you agree to arrange for the transportation of the pipe and drape to the venue.

\section{Venue Requirements}
If you have any questions about any of the following venue requirements, please do not hesitate to contact us for clarification.
\subsection{Mission Control Setup}
We will require two (2) rectangular tables and no more than two (2) chairs at Mission Control.
We ask that the tables are at least 30 inches deep and 60 inches wide.

\subsection{Power and Ethernet Access}
We will require two (2) power outlets at most 10 feet from Mission Control.
We will also require access to an Ethernet outlet, ideally within the same room as Mission Control.
Please contact us as soon as possible if either of the above is not possible.

\subsection{Field Layout and Spacing}
We will require seven (7) feet of space between the competition fields and the audience for our camera setup.

\subsection{Internet Firewall}
We will require the following websites (along with all subdomains and ports) to be unblocked on the day of setup and event:

\begin{centering}

\begin{tabular}{|c|}
    \hline
    \url{robotevents.com} \\
    \url{dwabtech.com} \\
    \url{vexscores.com} \\
    \url{roboticseducation.org}\\
    \url{youtube.com}\\ 
        \url{pretzel.rocks} \\
        \url{spotify.com}\\
        \url{18x18az.org} \\
    \hline
\end{tabular}

\end{centering}
\vspace{1em}

\noindent Some of these websites are required for posting results to RobotEvents and VEX Via, while others are for facilitating the livestream.
Our router's MAC address, if required to unblock the above websites, is:

\begin{centering}

    \begin{tabular}{|c|}
\hline
\texttt{fc:ec:da:7a:cc:2e} \\
\hline
\end{tabular}

\end{centering}

\subsection{Crowd Control Barriers}
If available, we would like to use crowd control barriers (such as those you might find in a lunch line) to protect our camera equipment.

\subsection{Pit Location}
Barring times where safety of teams can not be guaranteed indoors (such as a COVID-19 spike), team pits must be indoors.

\section{Equipment Transportation}
It is plausible we will need help transporting equipment from our base in Chandler to the venue during the day of setup.
As the event date approaches, we will be in contact regarding equipment transportation.

\section{Pricing}
A summary of our pricing options can be found below:
\begin{center}
    \begin{tabular}{|c|c|c|}
        \hline
        \textbf{Item} & \textbf{Includes} & \textbf{Price} \\
        \hline
                 & Field Control for:    &  \\
        Base Package & (2) Competition Fields, (1) Skills Field         & \$200 \\
                 & Livestream, TM Operation & \\
                 & Scoring Tablets          & \\
        \hline
        Large Event Package & Field Control for: & +\$100 \\
        & third Competition Field, second Skills Field & \\
        \hline
        Pipe and Drape & 70 feet of pipe and drape & +\$150, \\
                       & & transportation \\
        \hline
    \end{tabular}
\end{center}
If you are looking for something else not already listed, please do not hesitate to contact us.

\section{Contact Information}
Please contact us at \href{mailto:contact@18x18az.org}{contact@18x18az.org}.
% TODO: include emails
\end{document}
